From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-30 paper.tex
[minor] typos

Figures~\ref{fig:setup} and~\ref{fig:realSetup} illustrate the experimental
setup: a face-to-face child-robot interaction with an (autonomous) Aldebran's
{\sc nao} robot, in the presence of a facilitator (one of the researchers).

>>>>

Figures~\ref{fig:setup} and~\ref{fig:realSetup} illustrate the experimental
setup: a face-to-face child-robot interaction with an (autonomous) Aldebaran
{\sc nao} robot, in the presence of a facilitator (one of the researchers).
